---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```


[![Build Status](https://travis-ci.org/kota7/striprtf.svg?branch=master)](https://travis-ci.org/kota7/striprtf)
[![CRAN Status](http://www.r-pkg.org/badges/version/striprtf)](http://www.r-pkg.org/badges/version/striprtf)

# striprtf: Extract Text from RTF (Rich Text Format) File


## Installation

Install from CRAN.
```R
install.packages("striprtf")
```


Or install development version from Github using `devtools` library.
```R
devtools::install_github("kota7/striprtf")
```


## Usage

The package contains virtually only one function: `striprtf`, which parses
an Rich Text Format (RTF) file and extracts plain text out of it.

```{r}
library(striprtf)
x <- striprtf(system.file("extdata/king.rtf", package = "striprtf"))
head(x)
```

The package has also been tested with documents in East Asian languages.
```{r}
striprtf(system.file("extdata/amenimo.rtf", package = "striprtf"))
striprtf(system.file("extdata/mean.rtf", package = "striprtf"))
```


## References

The algorithm employed has been mainly discussed in a stack overflow thread
(http://stackoverflow.com/a/188877) and later refactored and implemented 
by Gilson Filho for python 3 (https://gist.github.com/gilsondev/7c1d2d753ddb522e7bc22511cfb08676).




